The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-08-23 script/en/chapters/crypto2020.tex
CT Book ed 12: Major update -- many changes, corrections, and additions during last 4 months

% ..........................................................................
% --------------------------------------------------------------------------
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%              Crypto 2020
% /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\newpage
\hypertarget{Chapter_Crypto2020}{}
\chapter{Crypto 2020 --- Perspectives for Long-Term Cryptographic
         Security}\index{security!long-term}
\label{Chapter_Crypto2020}
\begin{sloppypar}
(Johannes Buchmann, Erik Dahmen, Alexander May and Ulrich Vollmer, TU Darmstadt, May~2007)\\
\end{sloppypar}

@@

In 1978, Rivest, Shamir and Adleman suggested the
RSA\index{RSA} public key encryption and signature
schemes~\cite{rivest/shamir/adleman:1978}.  RSA is
still the most widely used public key scheme.  The
security of RSA depends on the difficulty of
factoring so-called RSA moduli which are products
of two large prime numbers.  In their 1978 paper,
the inventors of RSA suggested the use of RSA
moduli with 200 decimal digits for long-term
security.  Later, the company RSA Security
published a list of RSA moduli of increasing size,
the RSA challenge numbers.  RSA Security offered
prizes totaling \$ 635,000 for the factorization
of these numbers, cf.\
\url{www.rsasecurity.com/rsalabs/}.

In 2005, that is 27 years after the invention of
RSA, Bahr, Boehm, Franke, and Kleinjung from
Bochum University managed to factor a 200 digit
RSA challenge number
(\url{www.mat.uniroma2.it/~eal/rsa640.txt}).  A
key with size originally thought to be secure for
a very long time was broken with a computation
that took them just five months.  This illustrates
the tremendous progress factoring technology has
made within the last 30 years.  This progress is
based on break-through mathematical ideas --- e.g.\
the number field sieve proposed by John
Pollard --- as well as significant developments in
computer hardware and software implementation
technology.\footnote{%
Please compare chapter \ref{SecurityRSA}
\hyperlink{SecurityRSA}{Considerations regarding the
security of the RSA algorithm}, and especially chapters
\ref{nt:NoteFactorization} and \ref{FactorizationResearch}.
}

@@

For many years, the cryptography group at the
Technische Universit\"at Darmstadt and its spin-off,
the company FlexSecure (\url{www.flexsecure.de}),
have worked to provide these tools.  The
trust center software FlexiTrust which is employed
by the German National Root Certification
Authority and the German Country Signing Authority
offers an infrastructure within which
cryptographic schemes can be easily exchanged.
The open source library FlexiProvider\index{FlexiProvider} implements a
multitude of cryptographic schemes.  Lately, we
have intensified our research into ``Post Quantum
Cryptography''\index{cryptography!post quantum}\index{post-quantum computing}\index{PQC} seeking
cryptographic schemes which
remain secure even in the event that powerful
quantum computers are built.

@@

Encryption on the basis of lattice problems\index{encryption!lattice problems}
is very similar to that on the basis of
error-correcting codes.  Lattices are regular
structures of points in space.  For instance, the
points where the lines on squared paper cross form
a two-dimensional lattice.  For cryptographic
usage, the dimension of the lattices is chosen to
be much larger.  Encryption works as follows: The
plain-text is used to construct a lattice point
which is then slightly distorted in such a way
that it is no longer a lattice point, but close to
one.  Whoever knows a secret about the lattice is
able to find this lattice point in the vicinity of
the given point in space.  The lattice point in
turn yields the plain text.  A particularly
efficient lattice based encryption scheme is NTRU
Encrypt (\url{www.ntru.com})\index{encryption!lattice problems!NTR}.
However, because
NTRU was introduced fairly recently (in 1998), and
its specification underwent several changes due to
a variety of attacks, more cryptanalytic scrutiny
is required to achieve confidence in its security.

@@

Merkle uses in his construction so-called One-Time
Signatures: Each new signature requires a new
signing key and a new verification key.  The idea
Merkle had was to reduce the validity of many
verification keys using a hash tree to the
validity of a unique public hash value.  When
generating keys for the Merkle scheme one has to
determine the number of signatures one can make
with it in advance.  For a long time this seemed a
significant disadvantage.  In
\cite{buchmann/coronado/dahmen/doering/klintsevich:2006},
however, a variant of Merkle's scheme was proposed
which allows to compute $2^{40}$ signatures with a
single key pair.

@@

\putbib
\addcontentsline{toc}{section}{Bibliography}   % To add it in Contents and PDF-Navigation

>>>>

% $Id: 
% ..........................................................................
%              Crypto 2020
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{bibunit}[babalpha] %% alpha: Chapter bibliography shows authors abbreviation

\newpage
\hypertarget{Chapter_Crypto2020}{}
\chapter{Crypto 2020 --- Perspectives for Long-Term Cryptographic
         Security}\index{security!long-term}
\label{Chapter_Crypto2020}
\begin{sloppypar}
(\hyperlink{author_Johannes-Buchmann}{Johannes Buchmann},
 \hyperlink{author_Erik-Dahmen}{Erik Dahmen},
 \hyperlink{author_Alexander-May}{Alexander May}, and
 \hyperlink{author_Ulrich-Vollmer}{Ulrich Vollmer}, TU Darmstadt, May~2007)\\
\end{sloppypar}

@@

In 1978, Rivest, Shamir and Adleman suggested the
RSA\index{RSA} public key encryption and signature
schemes~\cite{rivest/shamir/adleman:1978}.  RSA is
still the most widely used public key scheme.  The
security of RSA depends on the difficulty of
factoring so-called RSA moduli which are products
of two large prime numbers.  In their 1978 paper,
the inventors of RSA suggested the use of RSA
moduli with 200 decimal digits for long-term
security.  Later, the company RSA Security
published a list of RSA moduli of increasing size,
the RSA Challenge numbers.  RSA Security offered
prizes totaling \$ 635,000 for the factorization
of these numbers, cf.\
\url{http://www.emc.com/emc-plus/rsa-labs/historical/the-rsa-challenge-numbers.htm}.

In 2005, that is 27 years after the invention of
RSA, Bahr, Boehm, Franke, and Kleinjung from
Bochum University managed to factor a 200 digit
RSA challenge number
(\url{www.mat.uniroma2.it/~eal/rsa640.txt}).  A
key with size originally thought to be secure for
a very long time was broken with a computation
that took them just five months.  This illustrates
the tremendous progress factoring technology has
made within the last 30 years.  This progress is
based on break-through mathematical ideas --- e.g.\
the number field sieve proposed by John
Pollard --- as well as significant developments in
computer hardware and software implementation
technology.\footnote{%
Please compare chapter \ref{SecurityRSA}
\hyperlink{SecurityRSA}{Considerations regarding the
security of the RSA algorithm}, and especially chapters
\ref{nt:NoteFactorization} and \ref{FactorizationResearch}.
For current cryptanalytical results against RSA and Dlog
see chapter \ref{Chapter_Dlog-FactoringDead}.
}

@@

For many years, the cryptography group at the
Technische Universit\"at Darmstadt and its spin-off,
the company FlexSecure (\url{www.flexsecure.de}),
have worked to provide these tools.  The
trust center software FlexiTrust which is employed
by the German National Root Certification
Authority and the German Country Signing Authority
offers an infrastructure within which
cryptographic schemes can be easily exchanged.
The open source library FlexiProvider\index{FlexiProvider} implements a
multitude of cryptographic schemes.  Lately, we
have intensified our research into ``Post Quantum
Cryptography'' (PQC)\index{cryptography!post quantum}\index{post-quantum computing}
seeking cryptographic schemes which
remain secure even in the event that powerful
quantum computers are built.

@@

Encryption on the basis of lattice problems\index{encryption!lattice problems}
is very similar to that on the basis of
error-correcting codes.  Lattices are regular
structures of points in space.  For instance, the
points where the lines on squared paper cross form
a two-dimensional lattice.  For cryptographic
usage, the dimension of the lattices is chosen to
be much larger.  Encryption works as follows: The
plain-text is used to construct a lattice point
which is then slightly distorted in such a way
that it is no longer a lattice point, but close to
one.  Whoever knows a secret about the lattice is
able to find this lattice point in the vicinity of
the given point in space.  The lattice point in
turn yields the plain text.  A particularly
efficient lattice based encryption scheme is NTRU
Encrypt (\url{https://www.securityinnovation.com/products/ntru-crypto})
\index{encryption!lattice problems!NTRU}.
However, because
NTRU was introduced fairly recently (in 1998), and
its specification underwent several changes due to
a variety of attacks, more cryptanalytic scrutiny
is required to achieve confidence in its security.

@@

Merkle uses in his construction so-called One-Time
Signatures: Each new signature requires a new
signing key and a new verification key.  The idea
Merkle had was to reduce the validity of many
verification keys using a hash tree to the
validity of a unique public hash value.  When
generating keys for the Merkle scheme one has to
determine the number of signatures one can make
with it in advance.  For a long time this seemed a
significant disadvantage.  In
\cite{buchmann/coronado/dahmen/doering/klintsevich:2006},
however, a variant of Merkle's scheme was proposed
which allows to compute $2^{40}$ signatures with a
single key pair.\footnote{%
  In JCT\index{JCT} you can find in the default perspective
  below the main menu item {\bf Visuals} several components and
  variants of this: the one-time signature WOTS+, the normal
  Merkle signature (MSS) and the extended Merkle signature
  scheme (XMSS).\index{Merkle signatur}\index{MSS}\index{XMSS}\index{WOTS}
}

@@

%------------------------------------------------------------------------------
\putbib[../de/references]
\addcontentsline{toc}{section}{Bibliography}
\end{bibunit}

\noindent All links in the article have been confirmed at July 15, 2016.
